Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
flesh out section about tracing

Prolog:
partially static datastructures are already built-in to Prolog and was built-into partial
evaluation from the beginning \cite{lloyd_partial_1991}.
 FP

>>>>

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the optimization of partially static data structures
was part of partial evaluation of Prolog programs from the beginning
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again completely disappear in the
residual program, which is equivalent to what our optimization does for an
imperative language.

 FP
